---
title: "Part7"
author: "Yuqing Feng"
date: "3/29/2023"
output: html_document
---

## Introduction

Serum metabolite abundance changes with chicken development

## Load packages

```{r}
library(vegan)
library(reshape2)
library(ggpubr)
library(openxlsx)
library(patchwork)
library(ComplexHeatmap)
library(ggplot2)
library(tibble)
library(dplyr)
library(circlize)
library(networkD3)
library(data.table)
```

### Figure 7A Residuals showing the difference in the microbe-metabolite association from different segments with absolute abundance.

```{r}
metab_log <- read.csv('../Data/08mixomics/log_transformed_metab.csv',header = T,row.names = 1)
AA_16S <- read.csv('../Data/02micro/output/L6_AA_16S.csv',header = T,row.names = 1)
AA_ITS <- read.csv('../Data/02micro/output/L6_AA_ITS.csv',header = T,row.names = 1)
Groups <- read.csv('../Data/02micro/output/Groups.csv',header = T)
AA_16S_all <- cbind(AA_16S,Groups$Segment)
AA_ITS_all <- cbind(AA_ITS,Groups$Segment)
colnames(AA_16S_all)[533] <- 'Segment'
colnames(AA_ITS_all)[604] <- 'Segment'
AA_16S_C <- AA_16S_all %>%
  filter(Segment=='Cecum') %>%
  select(-c(Segment))
AA_16S_D <- AA_16S_all %>%
  filter(Segment=='Duodenum') %>%
  select(-c(Segment))
AA_16S_I <- AA_16S_all %>%
  filter(Segment=='Ileum') %>%
  select(-c(Segment))
AA_16S_J <- AA_16S_all %>%
  filter(Segment=='Jejunum')%>%
  select(-c(Segment))
AA_ITS_C <- AA_ITS_all %>%
  filter(Segment=='Cecum') %>%
  select(-c(Segment))
AA_ITS_D <- AA_ITS_all %>%
  filter(Segment=='Duodenum') %>%
  select(-c(Segment))
AA_ITS_I <- AA_ITS_all %>%
  filter(Segment=='Ileum') %>%
  select(-c(Segment))
AA_ITS_J <- AA_ITS_all %>%
  filter(Segment=='Jejunum')%>%
  select(-c(Segment))
dist_16S_C <- vegdist(log2(AA_16S_C+1))
dist_16S_D <- vegdist(log2(AA_16S_D+1))
dist_16S_I <- vegdist(log2(AA_16S_I+1))
dist_16S_J <- vegdist(log2(AA_16S_J+1))
dist_ITS_C <- vegdist(log2(AA_ITS_C+1))
dist_ITS_D <- vegdist(log2(AA_ITS_D+1))
dist_ITS_I <- vegdist(log2(AA_ITS_I+1))
dist_ITS_J <- vegdist(log2(AA_ITS_J+1))
metab0 <- read.csv('../Data/08mixomics/log_transformed_metab.csv',header = T,row.names = 1)
metab <- metab0[,c(1,8,9,10,2:7,11:80)]
metab_dist <- vegdist(t(metab+1))
resid_16S_C <- data.frame(residuals(procrustes(dist_16S_C,metab_dist,scale = F)))
median(resid_16S_C[,1]) # 1.13
set.seed(1234)
cor_16S_C <- protest(dist_16S_C,metab_dist)
cor_16S_C$signif 
cor_16S_C$ss 
resid_16S_D <- data.frame(residuals(procrustes(dist_16S_D,metab_dist,scale = F)))
median(resid_16S_D[,1]) 
set.seed(1234)
cor_16S_D <- protest(dist_16S_D,metab_dist)
cor_16S_D$signif
cor_16S_D$ss
resid_16S_I <- data.frame(residuals(procrustes(dist_16S_I,metab_dist,scale = F)))
median(resid_16S_I[,1]) 
set.seed(1234)
cor_16S_I <- protest(dist_16S_I,metab_dist)
cor_16S_I$signif
cor_16S_I$ss 
resid_16S_J <- data.frame(residuals(procrustes(dist_16S_J,metab_dist,scale = F)))
median(resid_16S_J[,1])
set.seed(1234)
cor_16S_J <- protest(dist_16S_J,metab_dist)
cor_16S_J$signif 
cor_16S_J$ss 
resid_ITS_C <- data.frame(residuals(procrustes(dist_ITS_C,metab_dist,scale = F)))
median(resid_ITS_C[,1]) 
set.seed(1234)
cor_ITS_C <- protest(dist_ITS_C,metab_dist)
cor_ITS_C$signif 
cor_ITS_C$ss 
resid_ITS_D <- data.frame(residuals(procrustes(dist_ITS_D,metab_dist,scale = F)))
median(resid_ITS_D[,1]) 
set.seed(1234)
cor_ITS_D <- protest(dist_ITS_D,metab_dist)
cor_ITS_D$signif 
cor_ITS_D$ss 
resid_ITS_I <- data.frame(residuals(procrustes(dist_ITS_I,metab_dist,scale = F)))
median(resid_ITS_I[,1]) 
set.seed(1234)
cor_ITS_I <- protest(dist_ITS_I,metab_dist)
cor_ITS_I$signif 
cor_ITS_I$ss 
set.seed(1234)
cor_ITS_J <- protest(dist_ITS_J,metab_dist)
cor_ITS_J$signif 
cor_ITS_J$ss 
resid_ITS_J <- data.frame(residuals(procrustes(dist_ITS_J,metab_dist,scale = F)))
median(resid_ITS_J[,1]) 
all_residuals <- data.frame(resid_16S_C,resid_16S_D,resid_16S_I,resid_16S_J,resid_ITS_C,resid_ITS_D,resid_ITS_I,resid_ITS_J)
colnames(all_residuals) <- c('16S_Cecum','16S_Duodenum','16S_Ileum','16S_Jejunum','ITS_Cecum','ITS_Duodenum','ITS_Ileum','ITS_Jejunum')
all_res2 <- melt(all_residuals)
colnames(all_res2) <- c('Source','Residual')
all_res2$Sequencing <- rep(c('Bacteria','Fungi'),each = 320)
all_res2$Segment <- c(rep(c('Cecum','Duodenum','Ileum','Jejunum'),each = 80),rep(c('Cecum','Duodenum','Ileum','Jejunum'),each = 80))
all_res2$Segment <- factor(all_res2$Segment,levels = c('Duodenum','Jejunum','Ileum','Cecum'))
f7A <- ggplot(all_res2, aes(x = Segment, y = Residual, color = Segment)) +
  geom_boxplot(outlier.shape = NA) + 
  geom_jitter(alpha = 0.5,width = 0.2) +
  facet_grid(.~Sequencing) +
  theme_bw() +
  theme(legend.position = 'none',axis.text.x = element_text(angle = 45, vjust = 1,hjust = 1)) +
  scale_color_manual(values = c('#E64B35','#4DBBD5','#00A087','#3C5488'))+
  ylim(c(0,6))
f7A
```

### Figure S10 Cooccurrence profiles of microbes and metabolites. 

```{r}
all_res2_16S <- all_res2[all_res2$Sequencing=='Bacteria',]
all_res2_ITS <- all_res2[all_res2$Sequencing=='Fungi',]
pairwise.t.test(all_res2_16S$Residual,all_res2_16S$Segment,p.adjust.method = 'BH')
pva_16S <- data.frame(melt(pairwise.wilcox.test(all_res2_16S$Residual,all_res2_16S$Segment,p.adjust.method ='BH')$p.value))%>%
  na.omit()
pva_ITS <- data.frame(melt(pairwise.wilcox.test(all_res2_ITS$Residual,all_res2_ITS$Segment,p.adjust.method ='BH')$p.value))%>%
  na.omit()

d_16S_C <- read.xlsx('../Data/08mixomics/out_reorder/C_16S/beta.xlsx',sheet = 1) %>%
  select(-c('PC3'))
d_16S_D <- read.xlsx('../Data/08mixomics/out_reorder/D_16S/beta.xlsx',sheet = 1) %>%
  select(-c('PC3'))
d_16S_I <- read.xlsx('../Data/08mixomics/out_reorder/I_16S/beta.xlsx',sheet = 1) %>%
  select(-c('PC3'))
d_16S_J <- read.xlsx('../Data/08mixomics/out_reorder/J_16S/beta.xlsx',sheet = 1) %>%
  select(-c('PC3'))
d_ITS_C <- read.xlsx('../Data/08mixomics/out_reorder/C_ITS/beta.xlsx',sheet = 1) %>%
  select(-c('PC3'))
d_ITS_D <- read.xlsx('../Data/08mixomics/out_reorder/D_ITS/beta.xlsx',sheet = 1) %>%
  select(-c('PC3'))
d_ITS_I <- read.xlsx('../Data/08mixomics/out_reorder/I_ITS/beta.xlsx',sheet = 1) %>%
  select(-c('PC3'))
d_ITS_J <- read.xlsx('../Data/08mixomics/out_reorder/J_ITS/beta.xlsx',sheet = 1) %>%
  select(-c('PC3'))
bac_id <- read.xlsx('../Data/08mixomics/taxa.xlsx',sheet = 1)%>%
  select(c('ID','Genus','Phylum'))
fun_id <- read.xlsx('../Data/08mixomics/taxa.xlsx', sheet = 2) %>%
  select(c('ID','Genus','Phylum'))
d_16S_C2 <- merge(d_16S_C, bac_id, by.x = 'Taxa', by.y = 'ID',all.x = T)
d_16S_D2 <- merge(d_16S_D, bac_id, by.x = 'Taxa', by.y = 'ID',all.x = T)
d_16S_I2 <- merge(d_16S_I, bac_id, by.x = 'Taxa', by.y = 'ID',all.x = T)
d_16S_J2 <- merge(d_16S_J, bac_id, by.x = 'Taxa', by.y = 'ID',all.x = T)
# write.xlsx(d_16S_C2,'../Data/08mixomics/out_reorder/C_16S/taxa.xlsx', sheet = 1)
# write.xlsx(d_16S_D2,'../Data/08mixomics/out_reorder/D_16S/taxa.xlsx', sheet = 1)
# write.xlsx(d_16S_I2,'../Data/08mixomics/out_reorder/I_16S/taxa.xlsx', sheet = 1)
# write.xlsx(d_16S_J2,'../Data/08mixomics/out_reorder/J_16S/taxa.xlsx', sheet = 1)
d_ITS_C2 <- merge(d_ITS_C, fun_id, by.x = 'Taxa', by.y = 'ID',all.x = T)
d_ITS_D2 <- merge(d_ITS_D, fun_id, by.x = 'Taxa', by.y = 'ID',all.x = T)
d_ITS_I2 <- merge(d_ITS_I, fun_id, by.x = 'Taxa', by.y = 'ID',all.x = T)
d_ITS_J2 <- merge(d_ITS_J, fun_id, by.x = 'Taxa', by.y = 'ID',all.x = T)
# write.xlsx(d_ITS_C2, '../Data/08mixomics/out_reorder/C_ITS/taxa.xlsx', sheet = 1)
# write.xlsx(d_ITS_D2, '../Data/08mixomics/out_reorder/D_ITS/taxa.xlsx', sheet = 1)
# write.xlsx(d_ITS_I2, '../Data/08mixomics/out_reorder/I_ITS/taxa.xlsx', sheet = 1)
# write.xlsx(d_ITS_J2, '../Data/08mixomics/out_reorder/J_ITS/taxa.xlsx', sheet = 1)

metlin_cluster <- read.xlsx('../Data/07metabolome/clusters_metabolites.xlsx',sheet = 1) %>%
  select(c('Metlin','Cluster_new'))
head(metlin_cluster)
m_16S_C <- read.xlsx('../Data/08mixomics/out_reorder/C_16S/beta.xlsx',sheet = 2) %>%
  select(-c('PC3'))
m_16S_D <- read.xlsx('../Data/08mixomics/out_reorder/D_16S/beta.xlsx',sheet = 2) %>%
  select(-c('PC3'))
m_16S_I <- read.xlsx('../Data/08mixomics/out_reorder/I_16S/beta.xlsx', sheet = 2) %>%
  select(-c('PC3'))
m_16S_J <- read.xlsx('../Data/08mixomics/out_reorder/J_16S/beta.xlsx', sheet = 2) %>%
  select(-c('PC3'))
m_ITS_C <- read.xlsx('../Data/08mixomics/out_reorder/C_ITS/beta.xlsx',sheet = 2) %>%
  select(-c('PC3'))
m_ITS_D <- read.xlsx('../Data/08mixomics/out_reorder/D_ITS/beta.xlsx',sheet = 2) %>%
  select(-c('PC3'))
m_ITS_I <- read.xlsx('../Data/08mixomics/out_reorder/I_ITS/beta.xlsx', sheet = 2) %>%
  select(-c('PC3'))
m_ITS_J <- read.xlsx('../Data/08mixomics/out_reorder/J_ITS/beta.xlsx', sheet = 2) %>%
  select(-c('PC3'))

m_16S_C2 <- merge(m_16S_C, metlin_cluster, by.x = 'Metabolite', by.y = 'Metlin',all.x = T)
m_16S_D2 <- merge(m_16S_D, metlin_cluster, by.x = 'Metabolite', by.y = 'Metlin',all.x = T)
m_16S_I2 <- merge(m_16S_I, metlin_cluster, by.x = 'Metabolite', by.y = 'Metlin',all.x = T)
m_16S_J2 <- merge(m_16S_J, metlin_cluster, by.x = 'Metabolite', by.y = 'Metlin',all.x = T)
m_ITS_C2 <- merge(m_ITS_C, metlin_cluster, by.x = 'Metabolite', by.y = 'Metlin',all.x = T)
m_ITS_D2 <- merge(m_ITS_D, metlin_cluster, by.x = 'Metabolite', by.y = 'Metlin',all.x = T)
m_ITS_I2 <- merge(m_ITS_I, metlin_cluster, by.x = 'Metabolite', by.y = 'Metlin',all.x = T)
m_ITS_J2 <- merge(m_ITS_J, metlin_cluster, by.x = 'Metabolite', by.y = 'Metlin',all.x = T)

# write.xlsx(m_16S_C2,'../Data/08mixomics/out_reorder/C_16S/metab.xlsx',sheet = 1)
# write.xlsx(m_16S_D2,'../Data/08mixomics/out_reorder/D_16S/metab.xlsx',sheet = 1)
# write.xlsx(m_16S_I2,'../Data/08mixomics/out_reorder/I_16S/metab.xlsx',sheet = 1)
# write.xlsx(m_16S_J2,'../Data/08mixomics/out_reorder/J_16S/metab.xlsx',sheet = 1)
# write.xlsx(m_ITS_C2,'../Data/08mixomics/out_reorder/C_ITS/metab.xlsx',sheet = 1)
# write.xlsx(m_ITS_D2,'../Data/08mixomics/out_reorder/D_ITS/metab.xlsx',sheet = 1)
# write.xlsx(m_ITS_I2,'../Data/08mixomics/out_reorder/I_ITS/metab.xlsx',sheet = 1)
# write.xlsx(m_ITS_J2,'../Data/08mixomics/out_reorder/J_ITS/metab.xlsx',sheet = 1)

format_taxa <- function(d_16S_C2){
  d_16S_C2$Length <- sqrt((d_16S_C2$PC1)^2+ (d_16S_C2$PC2)^2)
  d_16S_C2$Rank <- rank(d_16S_C2$Length)
  temp1 <- nrow(d_16S_C2)
  temp1
  temp2 <- temp1 - 5
  for(i in 1:nrow(d_16S_C2)){
    if(d_16S_C2$Rank[i]>temp2){d_16S_C2$Genus2[i] <- d_16S_C2$Genus[i]}
    else(d_16S_C2$Genus2[i] <- '')
  }
  return(d_16S_C2)
}

d_16S_C2 <- format_taxa(d_16S_C2)
d_16S_D2 <- format_taxa(d_16S_D2)
d_16S_I2 <- format_taxa(d_16S_I2)
d_16S_J2 <- format_taxa(d_16S_J2)
d_ITS_C2 <- format_taxa(d_ITS_C2)
d_ITS_D2 <- format_taxa(d_ITS_D2)
d_ITS_I2 <- format_taxa(d_ITS_I2)
d_ITS_J2 <- format_taxa(d_ITS_J2)
h_16S_D <- read.table('../Data/08mixomics/out_reorder/D_16S/ranks.txt',header = T,row.names = 1) %>%
  rownames_to_column() %>%
  melt() %>%
  filter(value > quantile(value, 0.99)) %>%
  mutate(Annotation = 'Duodenum_16S') %>%
  rename('Metlin' = 'rowname') %>%
  rename('Taxa' = 'variable') 
h_16S_J <- read.table('../Data/08mixomics/out_reorder/J_16S/ranks.txt',header = T,row.names = 1) %>%
  rownames_to_column() %>%
  melt() %>%
  filter(value > quantile(value, 0.99)) %>%
  mutate(Annotation = 'Jejunum_16S')%>%
  rename('Metlin' = 'rowname') %>%
  rename('Taxa' = 'variable') 
h_16S_I <- read.table('../Data/08mixomics/out_reorder/I_16S/ranks.txt',header = T, row.names = 1) %>%
  rownames_to_column() %>%
  melt() %>%
  filter(value > quantile(value, 0.99)) %>%
  mutate(Annotation = 'Ileum_16S')%>%
  rename('Metlin' = 'rowname') %>%
  rename('Taxa' = 'variable') 
h_16S_C <- read.table('../Data/08mixomics/out_reorder/C_16S/ranks.txt',header = T, row.names = 1) %>%
  rownames_to_column() %>%
  melt() %>%
  filter(value > quantile(value, 0.99)) %>%
  mutate(Annotation = 'Cecum_16S') %>%
  rename('Metlin' = 'rowname') %>%
  rename('Taxa' = 'variable')
h_ITS_D <- read.table('../Data/08mixomics/out_reorder/D_ITS/ranks.txt',header = T,row.names = 1) %>%
  rownames_to_column() %>%
  melt() %>%
  filter(value > quantile(value, 0.99)) %>%
  mutate(Annotation = 'Duodenum_ITS') %>%
  rename('Metlin' = 'rowname') %>%
  rename('Taxa' = 'variable') 
h_ITS_J <- read.table('../Data/08mixomics/out_reorder/J_ITS/ranks.txt',header = T,row.names = 1) %>%
  rownames_to_column() %>%
  melt() %>%
  filter(value > quantile(value, 0.99)) %>%
  mutate(Annotation = 'Jejunum_ITS')%>%
  rename('Metlin' = 'rowname') %>%
  rename('Taxa' = 'variable') 
h_ITS_I <- read.table('../Data/08mixomics/out_reorder/I_ITS/ranks.txt',header = T, row.names = 1) %>%
  rownames_to_column() %>%
  melt() %>%
  filter(value > quantile(value, 0.99)) %>%
  mutate(Annotation = 'Ileum_ITS')%>%
  rename('Metlin' = 'rowname') %>%
  rename('Taxa' = 'variable') 
h_ITS_C <- read.table('../Data/08mixomics/out_reorder/C_ITS/ranks.txt',header = T, row.names = 1) %>%
  rownames_to_column() %>%
  melt() %>%
  filter(value > quantile(value, 0.99)) %>%
  mutate(Annotation = 'Cecum_ITS') %>%
  rename('Metlin' = 'rowname') %>%
  rename('Taxa' = 'variable')
all_metab_taxa <- rbind(h_16S_D,h_16S_J,h_16S_I,h_16S_C,
                        h_ITS_D,h_ITS_J,h_ITS_I,h_ITS_C)
le_metlin <- unique(all_metab_taxa$Metlin)
length(le_metlin)
all_metab_taxa2 <- all_metab_taxa
all_metab_taxa2$value <- 1
all_metab_taxa2$Taxa2 <- paste(all_metab_taxa2$Annotation,all_metab_taxa2$Taxa,sep = '-')
all_metab_taxa3 <- dcast(all_metab_taxa2[,c(1,3,5)],Metlin~Taxa2) 
all_metab_taxa3[is.na(all_metab_taxa3)] <- 0
rownames(all_metab_taxa3) <- all_metab_taxa3$Metlin
all_metab_taxa3 <- all_metab_taxa3[,-1]
taxa_seg <- strsplit(colnames(all_metab_taxa3),'-')
Taxa_Seg <- c()
for(i in 1:length(taxa_seg)){
  Taxa_Seg[i] <- taxa_seg[[i]][1]
}

data_for_order <- data.frame(colnames(all_metab_taxa3),colSums(all_metab_taxa3))
colnames(data_for_order) <- c('Genus','Number')
data_for_order$original <- 1:nrow(data_for_order)
for(i in 1:nrow(data_for_order)){
  data_for_order$cat1[i] <- strsplit(data_for_order$Genus,'-')[[i]][1]
}
data_for_order$cat1[data_for_order$cat1=='Duodenum_16S'] <- 'A'
data_for_order$cat1[data_for_order$cat1=='Duodenum_ITS'] <- 'B'
data_for_order$cat1[data_for_order$cat1=='Jejunum_16S'] <- 'C'
data_for_order$cat1[data_for_order$cat1=='Jejunum_ITS'] <- 'D'
data_for_order$cat1[data_for_order$cat1=='Ileum_16S'] <- 'E'
data_for_order$cat1[data_for_order$cat1=='Ileum_ITS'] <- 'F'
data_for_order$cat1[data_for_order$cat1=='Cecum_16S'] <- 'G'
data_for_order$cat1[data_for_order$cat1=='Cecum_ITS'] <- 'H'
data_for_order$cat1 <- factor(data_for_order$cat1,levels = c('A','B','C','D','E','F','G','H'),ordered = TRUE)
data_for_order2 <- data_for_order[order(data_for_order[,4], -data_for_order[,2]), ]
all_metab_taxa4 <- all_metab_taxa3[,data_for_order2$Genus]
data_for_order3 <- data.frame(rownames(all_metab_taxa3),rowSums(all_metab_taxa3))
colnames(data_for_order3) <- c('Metabolite','Number')
head(data_for_order3)
metlin_to_cluster <- openxlsx::read.xlsx('../Data/07metabolome/clusters_metabolites.xlsx',sheet = 1) %>%
  select(c('Metlin','Cluster_new'))
data_for_order3_2 <- merge(data_for_order3,metlin_to_cluster, by.x = 'Metabolite',by.y = 'Metlin', all.x = T)
data_for_order4 <- data_for_order3_2[order(data_for_order3_2$Cluster_new ,-data_for_order3_2[,2]),]
all_metab_taxa5 <- all_metab_taxa4[data_for_order4$Metabolite,]
Source1 <- c()
for(i in 1:nrow(data_for_order2)){
  Source1[i] <- strsplit(data_for_order2$Genus,'-')[[i]][1]
}
Number_Taxa <- colSums(all_metab_taxa5)
col_fun1 <- colorRamp2(c(1,72),c('white','#7E6148FF'))
col_fun2 <- colorRamp2(c(1,25),c('white','#8491B4FF'))
column_ha <- HeatmapAnnotation(Source = Source1,Number1 = Number_Taxa,
                               col = list(Number1 = col_fun1,
                                          Source = c('Duodenum_16S'='#E64B35','Jejunum_16S'='#E64B35','Ileum_16S'='#E64B35','Cecum_16S'='#E64B35',
                                                     'Duodenum_ITS'='#4DBBD5','Jejunum_ITS'='#4DBBD5','Ileum_ITS'='#4DBBD5','Cecum_ITS'='#4DBBD5')))
Number_metab <- rowSums(all_metab_taxa5)
rowname_ha <- HeatmapAnnotation( Number2 = Number_metab, Cluster = data_for_order4$Cluster_new,which = 'row',
                                 col = list(Cluster = c('C1'='#00A087','C2'='#3C5488','C3'='#F39B7F','C4'='#8491B4','C5'='#91D1C2','C6'='#B09C85'),Number = col_fun2))
pd1 <- Heatmap(all_metab_taxa5,name = 'Co-occurrence', top_annotation = column_ha,
               show_row_names = FALSE,show_column_names = FALSE,
               col = c('white','#E64B35'),
               cluster_columns = FALSE,
               cluster_rows = FALSE,
               border = TRUE,
               column_title = 'Genus',
               column_title_side = 'bottom',
               row_title = 'Metabolite',
               show_row_dend = FALSE, column_dend_reorder = unique(all_metab_taxa2$Taxa2),
               show_heatmap_legend = FALSE,
               right_annotation = rowname_ha) 
pd1


```

### Figure 7B The ratio of the top 1% co-occurrence possibilities in all microbe-metabolite interactions. Red cells represent more interactions between the metabolite and the microbe; blue cells represent fewer interactions between the metabolite and the microbe.

```{r}
all_metab_taxa_clu <- merge(all_metab_taxa, metlin_to_cluster, by = 'Metlin', all.x = T)
data_for_exact <- data.frame(table(all_metab_taxa_clu[,4:5]))
merge1 <- data.frame(table(metlin_to_cluster$Cluster_new)) %>%
  rename('Cluster' = 'Var1') %>%
  rename('Freq_me' = 'Freq')
merge2 <- data.frame(Source = c('Duodenum_16S','Jejunum_16S','Ileum_16S','Cecum_16S',
                                'Duodenum_ITS','Jejunum_ITS','Ileum_ITS','Cecum_ITS'),
                     Number = c(65,45,20,93,46,65,56,91)) %>%
  rename('Taxa' = 'Number')
data_for_exact2 <- merge(data_for_exact,merge1,by.x = 'Cluster_new',by.y = 'Cluster',all.x = T)
data_for_exact3 <- merge(data_for_exact2,merge2,by.x = 'Annotation',by.y = 'Source',all.x = T)
data_for_exact3$Ratio <- data_for_exact3$Freq/(data_for_exact3$Freq_me*data_for_exact3$Taxa) 
data_for_exact3$Annotation <- factor(data_for_exact3$Annotation,levels = rev(c('Cecum_ITS','Cecum_16S','Ileum_ITS','Ileum_16S',
                                                                               'Jejunum_ITS','Jejunum_16S','Duodenum_ITS','Duodenum_16S')))
f7B <- ggplot(data_for_exact3,aes(y = Cluster_new,x = Annotation,fill = Ratio * 100)) +
  geom_tile() +
  scale_fill_gradient2(low = '#3C5488',mid =  'white',high = '#E64B35',midpoint = 1) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  xlab('Source') +
  ylab('Cluster') +
  geom_text(data = data_for_exact3, aes(y = Cluster_new,x = Annotation, label = round(Ratio*100,2))) +
  scale_y_discrete(labels = c(1,2,3,4,5,6)) +
  scale_x_discrete(labels = rev(c("Cecum (F)","Cecum (B)",
                                  "Ileum (F)","Ileum (B)",
                                  "Jejunum (F)",'Jejunum (B)',
                                  'Duodenum (F)','Duodenum (B)')))

f7B
```

### Figure S11 Associations between genera in different phyla and metabolites in different clusters discovered using mmvec.

```{r}
h_D <- rbind(h_16S_D[,c(1,2)],h_ITS_D[,c(1,2)])
h_J <- rbind(h_16S_J[,c(1,2)],h_ITS_J[,c(1,2)])
h_I <- rbind(h_16S_I[,c(1,2)],h_ITS_I[,c(1,2)])
h_C <- rbind(h_16S_C[,c(1,2)],h_ITS_C[,c(1,2)])
taxa_id <- rbind(bac_id,fun_id)
convert_id_to_cat <- function(corr,metlin_cluster,taxa_id){
  corr1 <- merge(corr, metlin_cluster, by.x = 'Metlin', by.y = 'Metlin',all.x = T)
  corr2 <- merge(corr1, taxa_id[,c(1,3)], by.x = 'Taxa', by.y = 'ID',all.x = T)
  corr3 <- corr2[,c(3,4)]
  colnames(corr3) <- c('Target','Source')
  corr3$Count <- paste(corr3$Target,corr3$Source,sep = '-')
  require(dplyr)
  corr4 <- count(corr3, Count)
  require(stringr)
  corr5 <- data.frame(str_split_fixed(corr4$Count, '-', 2))
  corr5$number <- corr4$n
  colnames(corr5) <- c('Target','Source','Number')
  return(corr5)
}
hD2 <- convert_id_to_cat(h_D, metlin_cluster, taxa_id)
hJ2 <- convert_id_to_cat(h_J, metlin_cluster, taxa_id)
hI2 <- convert_id_to_cat(h_I, metlin_cluster, taxa_id)
hC2 <- convert_id_to_cat(h_C, metlin_cluster, taxa_id)
node_D <- data.frame(name = c(as.character(hD2$Source),
                              as.character(hD2$Target)) %>% unique())
node_J <- data.frame(name = c(as.character(hJ2$Source),
                              as.character(hJ2$Target)) %>% unique())
node_I <- data.frame(name = c(as.character(hI2$Source),
                              as.character(hI2$Target)) %>% unique())
node_C <- data.frame(name = c(as.character(hC2$Source),
                              as.character(hC2$Target)) %>% unique())
hD2$IDsource <- match(hD2$Source, node_D$name)-1 
hD2$IDtarget <- match(hD2$Target, node_D$name)-1
hJ2$IDsource <- match(hJ2$Source, node_J$name)-1 
hJ2$IDtarget <- match(hJ2$Target, node_J$name)-1
hI2$IDsource <- match(hI2$Source, node_I$name)-1 
hI2$IDtarget <- match(hI2$Target, node_I$name)-1
hC2$IDsource <- match(hC2$Source, node_C$name)-1 
hC2$IDtarget <- match(hC2$Target, node_C$name)-1
color_D <- 'd3.scaleOrdinal().domain(["Firmicutes", "Bacteroidetes","Proteobacteria",
"Ascomycota", "Basidiomycota", "Actinobacteria", "Verrucomicrobia", "Mortierellomycota",
"Epsilonbacteraeota","C1","C2","C3","C4","C5","C6"]).
range(["#8491B4", "#00A087" , "#91D1C2", "#4DBBD5", "#F39B7F", "#B09C85", "#B09C85", "#B09C85",
"#B09C85","#3C5488","#3C5488","#3C5488","#3C5488","#3C5488","#3C5488"])'
color_J <- 'd3.scaleOrdinal().domain(["Firmicutes", "Bacteroidetes","Proteobacteria",
"Ascomycota", "Basidiomycota", "Actinobacteria", "Verrucomicrobia", "Mortierellomycota",
"Epsilonbacteraeota","Mucoromycota","Glomeromycota","C1","C2","C3","C4","C5","C6"]).
range(["#8491B4", "#00A087" , "#91D1C2", "#4DBBD5", "#F39B7F", "#B09C85", "#B09C85", "#B09C85",
"#B09C85","#B09C85","#B09C85","#3C5488","#3C5488","#3C5488","#3C5488","#3C5488","#3C5488"])'
color_I <- 'd3.scaleOrdinal().domain(["Firmicutes", "Bacteroidetes","Proteobacteria",
"Ascomycota", "Basidiomycota", "Actinobacteria", "Verrucomicrobia", "Mortierellomycota",
"Epsilonbacteraeota","Mucoromycota","Glomeromycota","C1","C2","C3","C4","C5","C6"]).
range(["#8491B4", "#00A087" , "#91D1C2", "#4DBBD5", "#F39B7F", "#B09C85", "#B09C85", "#B09C85",
"#B09C85","#B09C85","#B09C85","#3C5488","#3C5488","#3C5488","#3C5488","#3C5488","#3C5488"])'
color_C <- 'd3.scaleOrdinal().domain(["Firmicutes", "Bacteroidetes","Proteobacteria",
"Ascomycota", "Basidiomycota", "Actinobacteria", "Verrucomicrobia", "Mortierellomycota",
"Epsilonbacteraeota","Mucoromycota","Glomeromycota","C1","C2","C3","C4","C5","C6"]).
range(["#8491B4", "#00A087" , "#91D1C2", "#4DBBD5", "#F39B7F", "#B09C85", "#B09C85", "#B09C85",
"#B09C85","#B09C85","#B09C85","#3C5488","#3C5488","#3C5488","#3C5488","#3C5488","#3C5488"])'
P_C1 <- sankeyNetwork(Links = hD2, Nodes = node_D,
                      Source = "IDsource", Target = "IDtarget",
                      Value = "Number", NodeID = "name", colourScale = color_D,
                      sinksRight=FALSE)
P_C2 <- sankeyNetwork(Links = hJ2, Nodes = node_J,
                      Source = "IDsource", Target = "IDtarget",
                      Value = "Number", NodeID = "name",  colourScale = color_J,
                      sinksRight=FALSE)
P_C3 <- sankeyNetwork(Links = hI2, Nodes = node_I,
                      Source = "IDsource", Target = "IDtarget",
                      Value = "Number", NodeID = "name", colourScale = color_I,
                      sinksRight=FALSE)
P_C4 <- sankeyNetwork(Links = hC2, Nodes = node_C,
                      Source = "IDsource", Target = "IDtarget",
                      Value = "Number", NodeID = "name", colourScale = color_C,
                      sinksRight=FALSE)

# saveNetwork(P_C1,'../Data/08mixomics/sankey/sankey_D.html')
# saveNetwork(P_C2,'../Data/08mixomics/sankey/sankey_J.html')
# saveNetwork(P_C3,'../Data/08mixomics/sankey/sankey_I.html')
# saveNetwork(P_C4,'../Data/08mixomics/sankey/sankey_C.html')
```


